### 2022-02-23 documentos/proofdiagonalization.tex
Now it's all microservices, I hope the fad persists.
We should get someone from Purdue to do this. They are the boilerplaters.
mod2 y comentarios

@@

$\sigma_{k l }=\sum_{j=0}^{1} (-1)^{j k }\dyad{j}{j\oplus l }$. In vectorized form

@@

\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\kket{j,j\oplus l },

@@

and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$},

@@

\kket{k,k\oplus l}=\frac{1}{2}\sum_{j=0}^{1} (-1)^{jk}\kket{\sigma_{jl}}.

@@

& = \frac{1}{2}\sum_{jkl m} \tau_{l m} (-1)^{l (j+k)} 
     \ddyad{j,j\oplus m}{k,k\oplus m}.

@@

@@

  \frac{1}{2}\sum_{jklm} \tau_{lm} (-1)^{l(j+k)} 
      \ddyad{j,k}{j\oplus m,k\oplus m}.

@@

@@

Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j\oplus
k$, then the Choi matrix reads

@@

    \frac{1}{2}\sum_{jk lm} \tau_{ lm} (-1)^{ l k} 
        \ddyad{j,j\oplus k}{j\oplus m,j\oplus m\oplus k},

@@

since $ (-1)^{j+j\oplus k} = (-1)^k $. To continue, we 

@@

The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
and fulfill the orthogonality relation 
$\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$. 
% \begin{equation}
% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
% \end{equation}
With this in mind, a $N$-qubit Pauli map can be written as 
% 
% 
% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
\begin{equation}
\hat{\mathcal{E}}_N = 
  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
\end{equation}
The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
\begin{align}
\kket{\sigma_{\vec{k}\vec{l} }}  & = 
   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \kket{\vec{j},\vec{j}\oplus \vec{l}},\\
%
 \kket{\vec{l},\vec{l}\oplus \vec{n}} & = 
   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
\end{align}
% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}

@@

& = \frac{1}{2}\sum_{\vec j\vec k\vec l \vec m} 
     \tau_{\vec l \vec m} (-1)^{\vec l (\vec j+\vec k)} 
     \ddyad{\vec j,\vec j\oplus \vec m}{\vec k,\vec k\oplus \vec m}.

@@

or more compactly $\vec{\lambda} = (H\otimes H/2)^{\otimes N} \vec{\tau}$. 

>>>>

\ddnote{Alejo, por fa revise q no se me fue un typo con el asunto de mod 2, ya corregí toda la notación y removi los otros comentarios, que ya fueron aclarados en la reunion y trataban de lo mismo}

@@

$\sigma_{k l }=\sum_{j=0}^{1} (-1)^{j k }\dyad{j}{j + l ( \text{mod}2) }$. In vectorized form

@@

\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\ket{j} \ket{j+l(\text{mod } 2) },

@@

and its inverse relation

@@

\ket{k}\ket{k+l (\text{mod } 2)}=\frac{1}{2}\sum_{j=0}^{1} (-1)^{jk}\kket{\sigma_{jl}}.

@@

& = \frac{1}{2}\sum_{jkl m} \tau_{l m} (-1)^{l (j+k)} \nonumber\\
     & \hspace{1cm} \times \ket{j}\ket{j +m  (\text{mod } 2)}\bra{k}\bra{k +m (\text{mod } 2)}.

@@

\begin{multline}

@@

  \frac{1}{2}\sum_{jklm} \tau_{lm} (-1)^{l(j+k)} \\
     \times \ket{j}\ket{k}\bra{j+ m(\text{mod}2)}\bra{k+m(\text{mod}2)}.

@@

\end{multline}

@@

Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j+
k (\text{mod} 2)$, then the Choi matrix reads
\begin{multline}

@@

    \frac{1}{2}\sum_{jk lm} \tau_{ lm} (-1)^{ l k} \\
       \times \ket{j}\ket{j +k(\text{mod } 2)}\bra{j+ m(\text{mod } 2)}\bra{j+ m+ k(\text{mod } 2)},

@@

since $ (-1)^{j+(j+ k (\text{mod} 2))} = (-1)^k $ \ddnote{Alejo, por fas checa esto, se me hace curioso que el modulo 2 solo este solo en la segunda suma del exponente}. To continue, we 

@@

\ddnote{Poner atencion a lo siguiente}
{\red[viejo y mal]The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
and fulfill the orthogonality relation 
$\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$.}
{\blue [nuevo y correcto y breve, la condicion de ortogonalidad no se usa explicitamente y es trivial]
The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }}$.
}
% \begin{equation}
% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
% \end{equation}
With this in mind, a $N$-qubit Pauli map can be written as 
% 
% 
% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
\begin{equation}
\hat{\mathcal{E}}_N = 
  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
\end{equation}
The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
\ddnote{corregir el angulo doble y tambien el oplus}
\begin{align}
\kket{\sigma_{\vec{k}\vec{l} }}  & = 
   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \ket{\vec{j}}\ket{\vec{j}+ \vec{l}(\text{mod}2)},\\
%
 \ket{\vec{l}}\ket{\vec{l}+ \vec{n}(\text{mod}2)} & = 
   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
\end{align}
% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}

@@

= \frac{1}{2}\sum_{\vec j\vec k\vec l \vec m} 
     \tau_{\vec l \vec m} (-1)^{\vec l (\vec j+\vec k)} \\
     \times\ket{\vec j}\ket{\vec j+\vec m (\text{mod}2)}\bra{\vec k}\bra{\vec k+\vec m(\text{mod}2)}.

@@

or more compactly $\lambda = (H\otimes H/2)^{\otimes N} \tau$. 
